Testing Gravity using Type Ia Supernovae Discovered by LSST

### 2018-11-01 doc/article.tex
continuing on and making sure notation of plots and text are consistent.

As distance indicators SNe~Ia
can provide peculiar velocities (expressed equivalently as peculiar magnitudes)
of their host galaxies \citep{2006PhRvD..73l3526H,2011ApJ...741...67D}.  Existing SN~Ia samples
have been used to test and ultimately find spatial correlations in peculiar velocities, may be attributed to the growth of structure
\citet{2015JCAP...12..033H, 2017JCAP...05..015H}.  However, the signal-to-noise is currently insufficient to perform a meaningful test of GR.

@@

\section{Supernova Peculiar Velocity Survey}
\citet{2017ApJ...847..128H} perform their analysis in Fourier space, 
where the Fisher information matrix of a random Gaussian field with mean zero and covariance $C(k)$ parameterized by $\lambda$ is
approximated by
\begin{equation}
F_{ij} = \frac{V}{2}\int \frac{d^3k}{(2\pi)^3} \text{Tr}\left[ C^{-1} \frac{\partial C}{\partial \lambda_i} C^{-1}
\frac{\partial C}{\partial \lambda_j} \right],
\end{equation}
where the covariance
\begin{equation}
C = P_{vv}(k) + \frac{\sigma^2}{n}
\end{equation}
has contributions from the power spectrum, noise in the velocity measurement, and the density of velocity probes
\citep{2017MNRAS.464.2517H}.   This equation is for the peculiar-velocity auto-correlation.

@@

This Appendix describes a new analysis used to project precisions on $f\sigma_8$ using peculiar velocities derived from SNe~Ia.
While there have been a number of articles on the subject,
our analysis brings a higher level of fidelity than sought by previous analyses.  We simulate SNe~Ia hosted by galaxies in a mock galaxy
catalog. The numbers of SNe are sufficiently small to allow fast evaluations of the likelihood, which enable the determination of parameter
posteriors using MCMC on reasonable computing timescales.   We can use our machinery to 
compare different survey parameters, such as redshift depth, total numbers of supernovae,
solid angle/survey geometry, and SN~Ia intrinsic magnitude dispersion.
We would like to
quantify the suppression of sample variance achieved when considering matter-densities and velocities 
within the same volume \citep{2007PhRvL..99h1301G}.
The cross-correlation between galaxy-count and peculiar-velocity surveys is not yet implemented but is a planned extension of this work.

@@

\section{Analysis}
The analysis of this article is  almost identical to that of \citet{2015JCAP...12..033H, 2017JCAP...05..015H}.   The peculiar magnitude correlation
function $\xi_{\delta m \delta m}$ expected from General Relativity starting with the CMB
matter density power spectrum is calculated using CAMB \citep{Lewis:2002ah}  assuming the same
cosmological parameters used for the Buzzard catalog.  Our model for the data covariance
is
\begin{equation}
C_{ij} = A\xi_{\delta m \delta m}(\mathbf{r_i},\mathbf{r_j}) + \frac{\sigma_M^2}{N_i} \delta_{ij} + \sigma^2_{NL}(z_i;\sigma_{v})\delta_{ij}.
\end{equation}
In this model, we treat the shape of the power spectrum $\xi$ as fixed and use the parameter $A$ to represent
deviations from General Relativity $A=1$.  This model is not sensitive to  the shape of
the power spectrum between gravitational models.  Nevertheless, for
convenience we say that our model gives $f\sigma_8 = A (f\sigma_8)^{GR}$, where $(f\sigma_8)^{GR}$ is the expectation
from General Relativity.  Special cases of modified gravity could give $A=1$, but inconsistency with $A=1$ is is evidence against General Relativity.
The final term includes extra magnitude dispersion produced by non-linear effects on velocity, parameterized with $\sigma_{v}$, such that
\begin{equation}
\sigma_{NL} = \frac{5}{\ln{10}} \frac{1+\bar{z}}{\bar{z}} \sigma_v,
\end{equation}
where $\bar{z}$ is the cosmological redshift of the host galaxy.
\section{Results of Subsets}

@@

The 
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{../outcosmo/pvlist.0.08.1234.1.0.2.pkl.png}
\caption{Confidence regions for the model parameters.  $A=(f\sigma_8)/(f\sigma_8)_{GR}$, $M$ is the supernova
absolute magnitude, $\sigma_M$ is the magnitude dispersion, and $\sigma_v$ is the non-linear contribution
to peculiar velocity.   The parameters for which I controlled the input, $M=0$ and $\sigma_M=0.08$~mag, are shown in dotted lines.
 Left: A survey truncated at $z_{max}=0.1$.  Right: A survey truncated at $z_{max}=0.15$.
\label{zmax:fig}}
\end{figure}

\begin{table}
   \centering
   %\topcaption{Table captions are better up top} % requires the topcapt package
   \begin{tabular}{|ccc|ccccc|} % Column formatting, @{} suppresses leading/trailing space
   \hline
$z_{max}$ & fraction & $\sigma_{SN}$ & $N_{gal}$ & $\bar{A}$ & $\sigma_A$ & $\sigma_A N_{gal}^{-0.5}$ & $\bar{A} \sigma_A^{-1} (18000/760)^{0.5}$ \\
\hline
0.20 & 0.20 & 0.08 & 2021 &   1.66 &   0.59 &  0.062 &  13.61 \\
0.10 & 0.30 & 0.08 & 429 &   1.26 &   0.51 &  0.120 &  12.09 \\
0.15 & 0.30 & 0.08 & 1215 &   1.42 &   0.55 &  0.074 &  12.48 \\
0.15 & 0.30 & 0.12 & 1215 &   1.97 &   0.92 &  0.061 &  10.36 \\
0.20 & 0.30 & 0.08 & 3023 &   1.34 &   0.43 &  0.057 &  15.16 \\
0.20 & 0.30 & 0.10 & 3023 &   1.40 &   0.54 &  0.047 &  12.68 \\
0.20 & 0.30 & 0.12 & 3023 &   1.48 &   0.72 &  0.037 &   9.95 \\
0.15 & 0.50 & 0.08 & 1982 &   1.12 &   0.37 &  0.069 &  14.93 \\
0.20 & 0.50 & 0.08 & 5015 &   1.13 &   0.30 &  0.054 &  18.54 \\
0.07 & 0.65 & 0.08 & 392 &   1.34 &   0.49 &  0.137 &  13.21 \\
0.10 & 0.65 & 0.08 & 873 &   0.89 &   0.35 &  0.087 &  12.57 \\
0.10 & 0.65 & 0.10 & 873 &   1.01 &   0.46 &  0.075 &  10.72 \\
0.15 & 0.65 & 0.08 & 2541 &   1.15 &   0.33 &  0.070 &  17.05 \\
0.15 & 0.65 & 0.10 & 2541 &   1.15 &   0.39 &  0.059 &  14.43 \\
0.15 & 0.65 & 0.12 & 2541 &   1.30 &   0.51 &  0.051 &  12.42 \\
0.20 & 0.65 & 0.08 & 6491 &   1.28 &   0.30 &  0.053 &  20.79 \\
0.20 & 0.65 & 0.10 & 6491 &   1.24 &   0.34 &  0.046 &  17.95 \\
0.20 & 0.65 & 0.12 & 6491 &   1.33 &   0.45 &  0.037 &  14.33 \\
0.07 & 1.00 & 0.08 & 563 &   1.16 &   0.36 &  0.135 &  15.55 \\
0.10 & 1.00 & 0.08 & 1294 &   0.91 &   0.28 &  0.091 &  15.96 \\
0.15 & 1.00 & 0.08 & 3870 &   1.00 &   0.24 &  0.066 &  20.00 \\
0.20 & 1.00 & 0.08 & 9901 &   1.18 &   0.23 &  0.050 &  24.38 \\
0.20 & 1.00 & 0.10 & 9901 &   1.06 &   0.25 &  0.042 &  20.33 \\
0.20 & 1.00 & 0.12 & 9901 &   1.09 &   0.28 &  0.040 &  19.13 \\
    \hline
   \end{tabular}
   \caption{Signal-to-noise in $A$ or equivalently $f\sigma_8$ for surveys parameterized by the maximum redshift $z_{max}$,
   the fraction of total supernovae in 10 years ``fraction'', intrinsic magnitude dispersion $\sigma_{SN}$.  The number of galaxies
   $N_{gal}$, the signal $\bar{A}$ and its uncertainty $\sigma_A$ are for the cosmoDC2 (v1.0) 760 sq.~deg. volume only.
   The uncertainty ``per'' supernova is given by  $\sigma_A N_{gal}^{-0.5}$.  The signal-to-noise, scaled to an LSST solid angle, is given as 
    $\bar{A} \sigma_A^{-1} (18000/760)^{0.5}$.
   \label{tab:booktabs}}
\end{table}

We consider two different scenarios cutting at different redshift depths $z_{max}=0.1$ and  $z_{max}=0.15$.  All the objects in the first
scenario are in the second scenario.  The results are shown in Fig.~\ref{zmax:fig}.  The points of interest are:
\begin{itemize}
\item There is a bias toward low $f\sigma_8$ for low-redshift ($z_{max}=0.1$).  Adding more supernova with increasing redshift
 decreases the bias  ($z_{max}=0.15$), and $A$ eventually approaches 1 ($z_{max}=0.2$ not shown).
 \item Based on the analysis of \citet{2017MNRAS.471.3135H}, I added an intrinsic velocity dispersion $\sigma_v$ (km~s$^{-1}$) due to non-linear effects.  This was not
 in Dragan's model.  My fit finds that this  dispersion is consistent with zero, not well constrained, and not strongly correlated with
 $A$.  The lack of covariance is consistent with Dragan's own tests.
 \item The fit intrinsic magnitude dispersion, on the other hand, is larger than the input $\sigma_M=0.08$ mag.  This  indicates that the catalogs
 contain 
 extra  velocity dispersion better attributed to intrinsic magnitude dispersion rather than correlated peculiar velocities.
\end{itemize}

\begin{figure}
\includegraphics[width=0.5\textwidth]{../outcosmo/pvlist.0.08.1234.1.0.1.pkl.png}
\includegraphics[width=0.5\textwidth]{../outcosmo/pvlist.0.08.1234.1.0.2.pkl.png}
\caption{Confidence regions for the model parameters.  $A=(f\sigma_8)/(f\sigma_8)_{GR}$, $M$ is the supernova
absolute magnitude, $\sigma_M$ is the magnitude dispersion, and $\sigma_v$ is the non-linear contribution
to peculiar velocity.   The parameters for which I controlled the input, $M=0$ and $\sigma_M=0.08$~mag, are shown in dotted lines.
 Left: A survey truncated at $z_{max}=0.1$.  Right: A survey truncated at $z_{max}=0.2$.
\label{zmax:fig}}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{../outcosmo/fracsnsig2_.png}
\includegraphics[width=0.5\textwidth]{../outcosmo/zmax_.png}
\caption{Confidence regions for the model parameters.  $A=(f\sigma_8)/(f\sigma_8)_{GR}$, $M$ is the supernova
absolute magnitude, $\sigma_M$ is the magnitude dispersion, and $\sigma_v$ is the non-linear contribution
to peculiar velocity.   The parameters for which I controlled the input, $M=0$ and $\sigma_M=0.08$~mag, are shown in dotted lines.
 Left: A survey truncated at $z_{max}=0.1$.  Right: A survey truncated at $z_{max}=0.15$.
\label{zmax:fig}}
\end{figure}

\begin{itemize}
\item Dragan: Is there some way that the formalism in your article breaks down at low-redshift?  I do remove very low-redshift objects at $z<0.01$,
which I think is conservative.
 \item Risa/Joe: Is there any reasons for the Buzzard catalog to not capture correlated peculiar velocities on small scales (box size to large?) nor capture
 non-linear velocities?  (I don't know how to translate a mass resolution of 2.7e10 $M_{\odot}/h$ into a spatial resolution!)
\end{itemize}

>>>>

As distance indicators SNe~Ia
can provide peculiar velocities (expressed equivalently as peculiar magnitudes)
of their host galaxies \citep{2006PhRvD..73l3526H,2011ApJ...741...67D}.  Existing SN~Ia samples
have been used to test and ultimately find spatial correlations in peculiar velocities, may be attributed to the growth of structure
\citet{2008MNRAS.389L..47A,2015JCAP...12..033H, 2017JCAP...05..015H}.  However, the STON is currently insufficient to perform a meaningful test of GR.

@@

\section{Supernova Peculiar Velocity Survey}
\citet{2017ApJ...847..128H} perform their analysis in Fourier space, 
where the Fisher information matrix of a random Gaussian field with mean zero and covariance $C(k)$ parameterized by $\lambda$ is
approximated by
\begin{equation}
F_{ij} = \frac{V}{2}\int \frac{d^3k}{(2\pi)^3} \text{Tr}\left[ C^{-1} \frac{\partial C}{\partial \lambda_i} C^{-1}
\frac{\partial C}{\partial \lambda_j} \right],
\end{equation}
where the covariance
\begin{equation}
C = P_{vv}(k) + \frac{\sigma^2}{n}
\label{cov:eq}
\end{equation}
has contributions from the power spectrum, noise in the velocity measurement, and the density of velocity probes
\citep{2017MNRAS.464.2517H}.   This equation is for the peculiar-velocity auto-correlation.

@@

This Appendix describes a new analysis used to project precisions on $f\sigma_8$ using peculiar velocities derived from SNe~Ia.
While there have been a number of articles on the subject,
our analysis brings a higher level of fidelity than sought previously.  We simulate SNe~Ia hosted by galaxies in a mock galaxy
catalog. The numbers of SNe are sufficiently small to allow fast evaluations of the likelihood, which enable the determination of parameter
posteriors using MCMC on reasonable computing timescales.   We can use our machinery to 
compare different survey parameters, such as redshift depth, total numbers of supernovae,
solid angle/survey geometry, and SN~Ia intrinsic magnitude dispersion.
We would like to
quantify the suppression of sample variance achieved when considering matter-densities and velocities 
within the same volume \citep{2007PhRvL..99h1301G}.
The cross-correlation between galaxy-count and peculiar-velocity surveys is not yet implemented but is a planned extension of this work.

@@

\section{Analysis}
The analysis is  almost identical to that of \citet{2015JCAP...12..033H, 2017JCAP...05..015H}.  
The peculiar magnitude is given by $\delta_m=(m - M) - \mu(z;H_0, \Omega_M, \Omega_\Lambda)$.  For our estimates we introduce one free parameter 
$\mathcal{M} = M - 5\log{H_0} + \text{const}$ and do not consider the other cosmological parameters, whose effects are relatively weak at low-redshift.

The peculiar magnitude correlation
function $\xi_{\delta m \delta m}$ expected from General Relativity acting on the CMB
matter density power spectrum is calculated using CAMB \citep{Lewis:2002ah}  assuming the same
cosmological parameters used for the cosmoDC2 catalog.  Our model for the data covariance
is
\begin{equation}
C_{ij} = A\xi_{\delta m \delta m}(\mathbf{r_i},\mathbf{r_j}) + \frac{\sigma_M^2}{N_i} \delta_{ij} + \sigma^2_{NL}(z_i;\sigma_{v})\delta_{ij},
\end{equation}
where $N_i$ is the number of SNe~Ia in galaxy $i$ and $\sigma_M$ is the intrinsic SN magnitude dispersion.
In this model, we treat the shape of the power spectrum $\xi$ as fixed and use the parameter $A$ to represent
deviations from General Relativity $A=1$.  This model is not sensitive to differences in the shapes
of  power spectra from different gravitational models.  Nevertheless, for
convenience we say that our model gives $f\sigma_8 = A (f\sigma_8)^{GR}$, where $(f\sigma_8)^{GR}$ is the expectation
from General Relativity.  Special cases of modified gravity could give $A=1$, but inconsistency with $A=1$ is is evidence against General Relativity.
The final term includes extra magnitude dispersion produced by non-linear effects on velocity, parameterized with $\sigma_{v}$, such that
\begin{equation}
\sigma_{NL} = \frac{5}{\ln{10}} \frac{1+\bar{z}}{\bar{z}} \sigma_v,
\end{equation}
where $\bar{z}$ is the cosmological redshift of the host galaxy.
We note that the CAMB calculation of $\xi$ includes non-linear corrections, which actually may be a bad thing for peculiar velocities \citep{2015MNRAS.454.3920H}. 
\citet{2015JCAP...12..033H} find that their results are insensitive to whether these corrections are included or not.

@@

The posterior of the parameters is sampled using MCMC.
The priors are positive and flat for $A$, flat for $M$, positive Cauchy(0.08, 0.5) for $\sigma_M$, and  positive Cauchy(0, 600 km~s$^{-1}$) for $\sigma_{v}$.

\section{Results of Subsets}

The projected STON in $f\sigma_8$ is calculated for different subsamples of the simulated data.
For each subsample  the mean  and standard deviation, $(\bar{A}, \sigma_A$) of the amplitude parameter is
determined.  The STON in $f\sigma_8$ for the subsample is thus  $\bar{A} \sigma^{-1}_A$, and that for a 18,000 sq.~deg. survey  is approximated by
$\sqrt{18000/760}\bar{A}\sigma^{-1}_A$.  The effective constraining power of a single supernova-based peculiar velocity in the subset is given by 
 $\sigma_A N_{gal}^{-0.5}$.

Different parameters describing the input simulated data define the subsamples, 
which are used to explore the range of possible survey strategies.   The varied parameters are the redshift range, $z_{max}$, intrinsic
magnitude dispersion, $\sigma_M$, and SN number density, $n = \phi n_{10}$, where $ n_{10}$ is the  10-year total number density.  In general a given point
of sky is not monitored over the full year, we take
$\phi \sim 0.65$ as an effective number density of discovered supernovae with light-coverage in 10 years.  
The fit posterior for one representative subsample, with input  $z_{max}=0.2$, $\sigma_M=0.08$, $\phi=0.65$, is shown in Figure~\ref{zmax:fig}.
For all subsamples, there is no evidence for non-convergence of the MCMC chains.  The parameter $\sigma_v$, not included in  \citet{2015JCAP...12..033H, 2017JCAP...05..015H},
is found to be consistent with zero, poorly constrained, and very weakly correlated with $A$.  Table~\ref{tab:subsets} gives the results for different subset analyses.

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{../outcosmo/pvlist.0.08.1234.0.65.0.2.pkl.png}
\caption{Confidence regions for the model parameters.  $A=(f\sigma_8)/(f\sigma_8)_{GR}$, $M$ is the supernova
absolute magnitude, $\sigma_M$ is the magnitude dispersion, and $\sigma_v$ is the non-linear contribution
to peculiar velocity.  This result is for the subset $z_{max}=0.2$, $\sigma_M=0.08$, $\phi=0.65$.  The dotted lines represent the inputs of the supernova
part of the simulation.
\label{zmax:fig}}
\end{figure}

\begin{table}
   \centering
   %\topcaption{Table captions are better up top} % requires the topcapt package
   \begin{tabular}{|ccc|ccccc|} % Column formatting, @{} suppresses leading/trailing space
   \hline
$z_{max}$ & $f$ & $\sigma_{M}$ & $N_{gal}$ & $\bar{A}$ & $\sigma_A$ & $\sigma_A N_{gal}^{-0.5}$ & $\bar{A} \sigma_A^{-1} (18000/760)^{0.5}$ \\
\hline
0.20 & 0.20 & 0.08 & 2021 &   1.66 &   0.59 &  0.062 &  13.61 \\
0.10 & 0.30 & 0.08 & 429 &   1.26 &   0.51 &  0.120 &  12.09 \\
0.15 & 0.30 & 0.08 & 1215 &   1.42 &   0.55 &  0.074 &  12.48 \\
0.15 & 0.30 & 0.12 & 1215 &   1.97 &   0.92 &  0.061 &  10.36 \\
0.20 & 0.30 & 0.08 & 3023 &   1.34 &   0.43 &  0.057 &  15.16 \\
0.20 & 0.30 & 0.10 & 3023 &   1.40 &   0.54 &  0.047 &  12.68 \\
0.20 & 0.30 & 0.12 & 3023 &   1.48 &   0.72 &  0.037 &   9.95 \\
0.15 & 0.50 & 0.08 & 1982 &   1.12 &   0.37 &  0.069 &  14.93 \\
0.20 & 0.50 & 0.08 & 5015 &   1.13 &   0.30 &  0.054 &  18.54 \\
0.07 & 0.65 & 0.08 & 392 &   1.34 &   0.49 &  0.137 &  13.21 \\
0.10 & 0.65 & 0.08 & 873 &   0.89 &   0.35 &  0.087 &  12.57 \\
0.10 & 0.65 & 0.10 & 873 &   1.01 &   0.46 &  0.075 &  10.72 \\
0.15 & 0.65 & 0.08 & 2541 &   1.15 &   0.33 &  0.070 &  17.05 \\
0.15 & 0.65 & 0.10 & 2541 &   1.15 &   0.39 &  0.059 &  14.43 \\
0.15 & 0.65 & 0.12 & 2541 &   1.30 &   0.51 &  0.051 &  12.42 \\
0.20 & 0.65 & 0.08 & 6491 &   1.28 &   0.30 &  0.053 &  20.79 \\
0.20 & 0.65 & 0.10 & 6491 &   1.24 &   0.34 &  0.046 &  17.95 \\
0.20 & 0.65 & 0.12 & 6491 &   1.33 &   0.45 &  0.037 &  14.33 \\
0.07 & 1.00 & 0.08 & 563 &   1.16 &   0.36 &  0.135 &  15.55 \\
0.10 & 1.00 & 0.08 & 1294 &   0.91 &   0.28 &  0.091 &  15.96 \\
0.15 & 1.00 & 0.08 & 3870 &   1.00 &   0.24 &  0.066 &  20.00 \\
0.20 & 1.00 & 0.08 & 9901 &   1.18 &   0.23 &  0.050 &  24.38 \\
0.20 & 1.00 & 0.10 & 9901 &   1.06 &   0.25 &  0.042 &  20.33 \\
0.20 & 1.00 & 0.12 & 9901 &   1.09 &   0.28 &  0.040 &  19.13 \\
    \hline
   \end{tabular}
   \caption{STON in $A$ or equivalently $f\sigma_8$ for surveys parameterized by the maximum redshift $z_{max}$,
   the fraction of total supernovae in 10 years ``fraction'', intrinsic magnitude dispersion $\sigma_{SN}$.  The number of galaxies
   $N_{gal}$, the signal $\bar{A}$ and its uncertainty $\sigma_A$ are for the cosmoDC2 (v1.0) 760 sq.~deg. volume only.
   The uncertainty ``per'' supernova is given by  $\sigma_A N_{gal}^{-0.5}$.  The STON, scaled to an LSST solid angle, is given as 
    $\bar{A} \sigma_A^{-1} (18000/760)^{0.5}$.
   \label{tab:subsets}}
\end{table}

In Fourier space, the data covariance is a combination of sample and shot noise (Eq.~\ref{cov:eq}).
In Figure~\ref{scaling:fig} the effective LSST STON for $z_{max}=0.2$ is plotted as a function of input $n \sigma^{-2}_M$.
The fact that the STON is not constant indicates that not of the subsamples is sample-variance limited, though its non-linearity
indicates that sample variance is non-negligible.

\begin{figure}
\includegraphics[width=0.5\textwidth]{../outcosmo/fracsnsig2_.png}
\includegraphics[width=0.5\textwidth]{../outcosmo/zmax_.png}
\caption{Left: Effective LSST STON for $z_{max}=0.2$ is plotted as a function of input  $n \sigma^{-2}_M$.
In both plots the result of a linear fit is plotted for reference. Right: For $\phi=1$ and $\sigma_M$, the  effective LSST STON as
a function of $z_{max}$>
\label{scaling:fig}}
\end{figure}

A SN peculiar survey benefits from greater redshift depth $z_{max}$ with the increase in volume and numbers of supernovae.  However,
peculiar velocity uncertainties increase with redshift and the follow-up of fainter high-redshift SNe requires more resources.  Table~\ref{tab:subsets}
shows that the effective worth of each supernova ($\sigma_A N_{gal}^{-0.5}$) diminishes with increasing survey depth.
The Table also shows that for $\sigma_M=0.08$~mag, the subsample with $z_{max}=0.1$ that has 1294 supernovae yields a STON of 15.96, whereas
a sample with $z_{max}=0.2$ that has (more) 2021 supernovae has a lower STON of 13.61.

%We consider two different scenarios cutting at different redshift depths $z_{max}=0.1$ and  $z_{max}=0.15$.  All the objects in the first
%scenario are in the second scenario.  The results are shown in Fig.~\ref{zmax:fig}.  The points of interest are:
%\begin{itemize}
%\item There is a bias toward low $f\sigma_8$ for low-redshift ($z_{max}=0.1$).  Adding more supernova with increasing redshift
% decreases the bias  ($z_{max}=0.15$), and $A$ eventually approaches 1 ($z_{max}=0.2$ not shown).
% \item Based on the analysis of \citet{2017MNRAS.471.3135H}, I added an intrinsic velocity dispersion $\sigma_v$ (km~s$^{-1}$) due to non-linear effects.  This was not
% in Dragan's model.  My fit finds that this  dispersion is consistent with zero, not well constrained, and not strongly correlated with
% $A$.  The lack of covariance is consistent with Dragan's own tests.
% \item The fit intrinsic magnitude dispersion, on the other hand, is larger than the input $\sigma_M=0.08$ mag.  This  indicates that the catalogs
% contain 
% extra  velocity dispersion better attributed to intrinsic magnitude dispersion rather than correlated peculiar velocities.
%\end{itemize}

%\begin{figure}
%\includegraphics[width=0.5\textwidth]{../outcosmo/pvlist.0.08.1234.1.0.1.pkl.png}
%\includegraphics[width=0.5\textwidth]{../outcosmo/pvlist.0.08.1234.1.0.2.pkl.png}
%\caption{Confidence regions for the model parameters.  $A=(f\sigma_8)/(f\sigma_8)_{GR}$, $M$ is the supernova
%absolute magnitude, $\sigma_M$ is the magnitude dispersion, and $\sigma_v$ is the non-linear contribution
%to peculiar velocity.   The parameters for which I controlled the input, $M=0$ and $\sigma_M=0.08$~mag, are shown in dotted lines.
% Left: A survey truncated at $z_{max}=0.1$.  Right: A survey truncated at $z_{max}=0.2$.
%\label{zmax:fig}}
%\end{figure}
%

%
%\begin{itemize}
%\item Dragan: Is there some way that the formalism in your article breaks down at low-redshift?  I do remove very low-redshift objects at $z<0.01$,
%which I think is conservative.
% \item Risa/Joe: Is there any reasons for the Buzzard catalog to not capture correlated peculiar velocities on small scales (box size to large?) nor capture
% non-linear velocities?  (I don't know how to translate a mass resolution of 2.7e10 $M_{\odot}/h$ into a spatial resolution!)
%\end{itemize}
